On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-23 article/ms.tex
The best damn paper ever written

	\todo{1. Calculate mass of Eu expected form NSM within 15 kpc sphere throughout age of universe. DONE 2. Calculate  mass of Eu in each 0.8 solar mass star DONE. 3. How many we expect in that 15 kpc sphere throughout universe? 4. Multiply by fraction of LAMOST giants/number of giant stars in Milky Way, assuming star formation rate and typical IMF etc. 5. Repeat for CCSN. 6. Since estimated number from CCSN is only 4 giant stars in LAMOST, then state how long it would take to produce 60 r-process stars in LAMOST: orders of magnitude longer than the age of the universe.}

@@

	The total known mass of Europium exhibited in these 47 stars was then calculated:
	\begin{equation}
	Eu_{\rm{Mass}} = 47*Eu_{\textrm{Atomic\,\,mass}}*N_{\textrm{Eu}}
	\end{equation}
	Where:
	\begin{equation}
	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\
	\end{equation}
	\begin{equation}
	N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}
	\end{equation}
	The number of Hydrogen atoms was approximated from the Hydrogen atomic mass, and the assumption was made that a giant star will be composed of $\approx$75\% Hydrogen and each star possesses an average mass of $\approx 0.8\ M_{\odot}$. These assumption mean that a Europium mass of $9.3 \times 10^{20}$ kilograms is required to be present in the star for it to be deemed 'enhanced'.

>>>>

@@

	The total known mass of Europium exhibited in these 47 stars was then calculated:
	\begin{equation}
	Eu_{\rm{Mass}} = 47*Eu_{\textrm{Atomic\,\,mass}}*N_{\textrm{Eu}}
	\end{equation}
	Where:
	\begin{equation}
	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}
	\end{equation}
	\begin{equation}
	N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}
	\end{equation}
	The number of Hydrogen atoms was approximated from the Hydrogen atomic mass, and the assumption was made that a giant star will be composed of $\approx$75\% Hydrogen and each star possesses an average mass of $\approx 0.8\ M_{\odot}$. These assumption mean that a Europium mass of $9.3 \times 10^{20}$ kilograms is required to be present in the star for it to be deemed 'enhanced'.
